# Introduction



```{r, echo=FALSE, eval=knitr::is_html_output(), results='asis'}

# HTML output

cat('
<blockquote class="my-quote">
  <p>
"My aim here is to contribute something to the improvement of learning in our school district; or any school district.  My goal is to build a collabrative community helping each other find better and better ways of using data to guide, improve and govern their systems of learning.   

I look forward to the day when everyone at every level is comfortable thinking of ways to improve, trying the changes on a small scale, and plotting the results to see if the changes worked.  This method encourages the study of different ideas of learning and administration (inputs) and their impact on the results observed (outputs) ***at the local level.***  

The important question is never, "Did a method work somewhere?" but always "Does it work here (and why)?"

Those interested in using data to help improve learning in their district please feel free to contact me."
</p>
  <p class="quote-author">          — Dan Swart</p>
  <p class="quote-description" style="text-align: right; font-style: italic;"></p>
</blockquote>
')

```



```{r, echo=FALSE, eval=knitr::is_latex_output(), results='asis'}

# PDF quote code (LaTeX)

cat('
\\begin{tcolorbox}[colback=white, colframe=teal, boxrule=2pt, arc=4pt]
  \\begin{minipage}{0.95\\textwidth}
    \\raggedright
    \\Large{"My aim here is to contribute something to the improvement of learning in our school district; or any school district.  My goal is to build a collabrative community helping each other find better and better ways of using data to guide, improve and govern their systems of learning.}

    \\vspace{12pt}  % Add vertical space here

    \\Large{I look forward to the day when everyone at every level is comfortable thinking of ways to improve, trying the changes on a small scale, and plotting the results to see if the changes worked.  This will encourage the study of different ideas of learning and administration (inputs) and their impact on the results observed (outputs) \\textbf{\\textit{at the local level.}}}
  
    \\vspace{12pt}  % Add vertical space here
  
     \\Large{The important question is never, Did a method work somewhere? but always, Does it work here (and why)?}

    \\vspace{12pt}  % Add vertical space here

    \\Large{Those interested in using data to help improve learning in their district please feel free to contact me."}
  \\end{minipage}\\\\[5pt]
  \\begin{minipage}{0.95\\textwidth}
    \\raggedleft
    \\Large{Dan Swart}\\\\
    \\emph{}
  \\end{minipage}
\\end{tcolorbox}
')

```

\vspace{0.75in}


A WORD ABOUT THE DATA

The Texas Education Agency defines, and often re-defines the metrics and categories supplied.  When a new metric is introduced you will see measurements begin in the year introduced.  Measurements cease when discontinued by TEA.  No Standardized Scores were issued for the year 2020 and, accordingly, some charts show a gap for that year.

\vspace{0.5in}

This book was created from Quarto and executable code.

A citation [@example2023].
<br> <br> <br>
